Symbolic Abstract Data Type Inference

### 2015-07-06 algorithm.tex
starting top-down presentation

\begin{figure}
\begin{lstlisting}
Min := $\emptyset$
while (true) {
  $B_i$ := $ \set{ h \in B : \weight(h) = i }$;
  MinTemp := Min $\cup$ Min($B_i$)
  if ( MinTemp = Min )
    break;
  Min := MinTemp
}
return $\neg$Formula(Min);
\end{lstlisting}
\caption{The algorithm solving the symbolic ADT inference problem for a given ADT $A$. $B$ denotes the bounded complement of $\ker A$ and $\uparrow$\texttt{Min} denotes the upward closure w.r.t. $\preceq$ of a given set of histories. The procedure $\texttt{Min}(X)$ returns the $\preceq$-minimal elements of the set of histories $X$ and $\texttt{Formula}(X)$ returns a history formula which holds exactly for the histories in the upward closure of $X$.} 
\label{fig:algorithm}
\end{figure}

>>>>

\begin{figure}
\begin{lstlisting}
Min := $\emptyset$
while (true) {
  $B_i$ := $ \set{ h \in B : \weight(h) = i }$;
  MinTemp := Min $\cup$ Min($B_i$)
  if ( MinTemp = Min )
    break;
  Min := MinTemp
}
return $\neg$Formula(Min);
\end{lstlisting}
\caption{The algorithm solving the symbolic ADT inference problem for a given ADT $A$, where $B$ denotes the bounded complement of $\ker A$. The procedure $\texttt{Min}(X)$ returns the $\preceq$-minimal elements of the set of histories $X$ and $\texttt{Formula}(X)$ returns a history formula which holds exactly for the histories in the upward closure of $X$.} 
\label{fig:algorithm}
\end{figure}
